---
title: "cookbook"
author: "Fabricio Dujardin"
date: "7/31/2017"
output: 
  html_document:
    keep_md: true
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
#CookBook
The data set that is used comes from: https://d396qusza40orc.cloudfront.net/getdata%2Fprojectfiles%2FUCI%20HAR%20Dataset.zip
One of the most exciting areas in all of data science right now is wearable computing. The dataset is exactly this.

##Identifiers

* subject - The ID of the test subject
* activity - The type of activity performed when the corresponding measurements were taken

##Measurements
The measurements come from the features dataset. We are interested in the mean and std from these.

```{r}
library(data.table)
library(knitr)
features        <- data.table(read.table("./UCI HAR Dataset/features.txt",stringsAsFactors = F))
kable(features)
```

##Activity
There are 6 activies as follow, and the names are straight forward for the description:

```{r}

activity_labels <- data.table(read.table("./UCI HAR Dataset/activity_labels.txt",stringsAsFactors = F))
activity_labels
```


